---
output: github_document
---

```{r setup, include = FALSE}
library(redbull)
```
# redbull

The `redbull` package contains `ggplot2` colour themes for use in Red Bull Data Science projects.

## Installation

You can install `redbull` from github with:

```r
# You need to install the 'devtools' package first
devtools::install_github("deathbydata/redbull")
```

## The Palettes

There are several colours and palettes built in to the package. Additions and modifications are welcomed! See the [`palettes.R`](/R/palettes.R) file for the details.

* `redbull` (default)
* `rbfull`
* `rbcool`
* `rbwarm`
* `rbyellowgrey`
* `bloomberg`
* `bloombergfull`

## Usage

Usage is through the functions `scale_fill_redbull` and `scale_colour_redbull` depending on your plot aesthetic.

```{r scale_redbull}
library(ggplot2)
library(redbull)
library(magrittr)

theme_set(theme_bw())

# Using colour aesthetic (points/lines)
mtcars %>% 
  ggplot(aes(x = wt, y = mpg, colour = as.factor(cyl))) + 
  geom_point(size = 4, alpha = 0.75) + 
  scale_colour_redbull() +
  style_redbull()

# Using fill aesthetic (bars/areas)
mtcars %>% 
  ggplot(aes(x = as.factor(carb), fill = as.factor(carb))) + 
  geom_bar() + 
  scale_fill_redbull("rbfull") +
  style_redbull()
```

You can use `discrete = FALSE` if you have continuous values. `reverse = TRUE` will flip the direction of the colours in the palette.

```{r discrete and reverse}
mtcars %>% ggplot(aes(x = disp, y = wt, colour = hp)) + 
  geom_point(size = 4.5, colour = "black") +
  geom_point(size = 4) + 
  scale_color_redbull("rbwarm", discrete = FALSE, reverse = TRUE) +
  style_redbull() +
  ggtitle("Relationship between engine weight and displacement") +
  xlab("Engine displacement (cc)") +
  ylab("Engine weight (?)")
```

For discrete scales you can select the behaviour when there are more levels of your factor than palette colours using the `rep` parameter.

```{r rep parameter}
mtcars %>% 
  ggplot(aes(x = as.factor(carb), fill = as.factor(carb))) + 
  geom_bar() + 
  scale_fill_redbull("rbyellowgrey", rep = TRUE)

mtcars %>% 
  ggplot(aes(x = as.factor(carb), fill = as.factor(carb))) + 
  geom_bar() + 
  scale_fill_redbull("rbyellowgrey", rep = FALSE)
```
